Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-09 paper/paper.tex
pass on abstract and intro

%% JavaScript (\js{}) is a popular programming language for the
%% web. Finding errors in JS runtime engines is an important problem.
\begin{abstract}
JavaScript is a very popular programming language today. Checking
reliability of JavaScript engines is therefore an important
problem. This paper reports on a study to assess reliability of
JavaScript engines by leveraging the rich diversity of open-source
implementations. We explored two methods for that---test
transplantation and cross-engine differential testing. Test
transplatation evaluates the effects of running test suites of a given
engine in another engine. Cross-engine differential testing evaluates
the effects of fuzzing existing inputs and then comparing the output
produced by different engines with a differential oracle. Our results
indicate that \Fix{...}
\end{abstract}

@@

JavaScript (\js{}) is today one of the most popular programming
languages around~\cite{business-insider,stackify}, with significant
penetration in various segments including, web development, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification
and implementations. It is natural to expect that such improvements
lead to sensible implementation changes. Even small changes can have
high impact. For example, in October 2014 a new attribute added to
Array objects caused a bug in the MS Outlook Calendar web app under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging as specifications are incomplete and evolve
frequently. Consequently, it is often non-trivial to assess if a test
fails because of a bug or because of some other reason. For example, a
test may fail because the engine does not fully implement some
feature. The publicly-available Kangax compatibility
table~\cite{kangax} highlights this problem--it relates features of
\js\ with the engines that support them. As another example of a
failure that is not caused by a bug, a test that passes in one engine
could legitimately fail in another engines because of some undefined
behavior in the spec\footnote{These cases of undefined behavior can be
  localized by searching for the string ``implementation-dependent''
  in the ES6 spec document~\cite{ecmas262-spec}.}.

@@

%% WHAT WE DID
The goal of this paper is to assess reliability of popular
\js\ engines. The paper reports the results of a study that evaluates
the effectiveness of two complementary diversity-aware techniques to
find bugs in \js\ engines. \emph{Test transplantation} leverages
diversity of test cases to find bugs. It evaluates the effects that
running \js{} test files from a given engine have in detecting bugs in
other engines. The intuition is that developers design test cases
differently; hence replaying the test in a different engine may reveal
unanticipated problems. \emph{Cross-engine differential testing}
evaluates the ability of leveraging diversity of engine
implementations to find bugs. More precisely, it fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. One of
various causes of output discrepancy is a bug. It is worth noting that
Differential Testing~\cite{Brumley-etal-ss07} (DT) has been applied in
a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files\footnote{These files are created with the grammar-based fuzzer
  jsfunfuzz~\cite{jsfunfuzz}. Look for option ``compare\_jit'' from funfuzz.} against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across different configurations of the same build (\eg{}, enabling or
not eager JIT compilation). They use this technique since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
contrast, cross-engine differential testing--the technique used in
this work--checks functional correctness by comparing the output
produced by \emph{different engines} on a fuzzed
input~\cite{patra2016learning} as opposed to different builds of the
same engine. This approach has not been
popularized, certainly, because it is still not practical to fully automate--a
number of legitimate reasons exist, other than a bug, for a test
execution to manifest discrepancy (see
Table~\ref{tab:false-positives}). This study quantifies human effort
to find these bugs using this method.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed.}
  \begin{tabular}{cccr}
    \toprule
    Team & Name & URL & \# Stars \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{3300+} \\
    Google & \veight{} & \cite{v82018repo} & 9800+ \\
%    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ \\
%    Moddable & XS & \cite{xs2018repo} & 140+ \\
    %% \midrule
    %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{1100+} \\
   \bottomrule     
  \end{tabular}
\end{table}

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the offical
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. Table~\ref{tab:test-suites} shows the breakdown of
tests we considered. Overall, we found a total of \totfiles{} JS
files. We did not consider tests from the \chakra{} repository because
they depend on non-portable objects. Notice that the number of tests
in \veight\ is low. That happens because many tests in \veight{} are
inherited from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. For all engines engines
we found test using non-portable functions that we detected by running
the test on a different engine. We needed to discard those.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,021 \\
    \smonkey\ & \cite{mozilla} & 2,116 \\
    \veight{} & \cite{v8} & 57 \\
    \midrule    
    Duktape & \cite{duktape} & 921 \\ 
    JerryScript & \cite{jerryscript} & 1,878 \\
    JSI & \cite{jsi} & 63 \\
    Tiny-js & \cite{tinyjs} & 37 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} \\
   \bottomrule     
  \end{tabular}
\end{table}

% For example to run the JerryScript tests it was necessary 
% use the unit-test package to run it, but with our changes we added the assertion
% does not have an assertion in the test file
% \Fix{add code to explain}

@@

Generational fuzzers are typically grammar-based. These fuzzers
generate a new file using the grammar of the language whose inputs
should be fuzzed. Intuitively, those fuzzers implement a traversal of
the production rules of the input grammar to create syntax trees,
which are then pretty-printed. Consequently, this approach produces
inputs that are syntactically valid by construction. We analyzed four
grammar-based fuzzers--Grammarinator~\cite{grammarinator},
jsfunfuzz~\cite{jsfunfuzz},
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
were effective out of the box. For example, we produced 100K inputs
with Grammarinator and only \Fix{X} of those were valid. With
Megadeth, we were able to produce \Fix{Y, Y$>$Y?}  valid inputs as it
contains some heuristics to circumvent violations of certain type
rules such as \Fix{variable used must be defined?}. Nonetheless,
running those inputs in our infrastructure we were unable to find
discrepancies. Inpecting those inputs, we realized that they reflected
very simple scenarios. To sum, a high percentage of inputs that
Grammarinator and Megadeth generated were semantically-invalid that we
needed to discard whereas the valid inputs manifested no
discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
that, in addition to the issues mentioned above, it produces inputs
that use functions that are only available in the SpiderMonkey
engine. We would need either to mock those functions in other engines
or to discard those tests. Considering
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
publicly available. One fundamental issue associated with generational
fuzzers in our context is that the tests they produce do not contain
assertions; to enable the integration of this kind of fuzzers in our
infrastructure, we would need to look for discrepancies across
compiler messages.  All in all, although grammar-based fuzzers have
been shown effective to find real
bugs~\cite{Holler:2012:FCF:2362793.2362831}, generating valid inputs,
albeit promising conceptually, still requires some engineering
effort. For this reason, we did not consider those fuzzers in this
study.

@@

Mutational fuzzers can be either white-box or black-box. White-box
mutational fuzzers are typically coverage-based. American Fuzz Loop
(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
kind of fuzzers. These fuzzers run tests inputs against instrumented
versions of the program under testing with the typical goal of finding
univeral errors like crashes and buffer overflows. The instrumentation
adds code to collect branch coverage and to monitor specific
properties\footnote{There are options in the clang toolchain to build
  programs with fuzzing instrumentation~\cite{libfuzzer}. clang
  provides several sanitizers for property
  checking~\cite{clang-documentation}.}. AFL use coverage to determine
inputs that uncover a new branch and hence should be fuzzed more
whereas libFuzzer uses evolutionary generation--it tries to minimize
the distances to still-uncovered branches of the program. AFL takes
the instrumented program binary (say, a JS engine) and one seed input
to that program (say, a JS program) and produces on output
fault-revealing inputs, if found. Considering our context of
application, we needed to instrument one runtime engine for fuzzing;
we chose v8. Unfortunately, we found that most of the inputs produced
by AFL violate the JS grammar. Furthermore, the fuzzing task can take
days for a single seed input and there is no simple way to guide the
exploration\footnote{Exchanged emails with the tool author.}. That
happens because the fuzzer aims to explore the entire decision tree
induced from the engine's main function, including the branches
associated with the higher layers of the compiler (\eg{}, lexer and
parser). It is worth mentioning that Google mitigates that problem
with libFuzzer by asking developers to create fuzz targets for
specific program
functions\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
that approach has shown very effective, it requires domain knowledge
to create the calling context to invoke the fuzz target. For those
reasons, coverage-based fuzzers were not considered in this study.

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
\emph{existing} inputs randomly. The strenght of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose \radamsa\ and
\quickfuzz\ \Fix{...elaborate...} \Mar{I mention below that these
  fuzzers ``only make valid changes in literals of the
  language''. Please confirm and explain that still this is
  interesting!}

\subsubsection{Differential Testing Infrastructure}
\label{sec:design}

@@

Recall that a warning can be manifested for reasons other than a bug
and there is no clear way to distiguish those cases automatically (see
Table~\ref{tab:false-positives}). A human needs to inspect the warning
to diagnose the discrepancy. To facilitate inspection, the
infrastructure prioritize these warnings and clusters them in
groups. Considering prioritization, we classified warnings in two
kinds, reflecting their likelihood to manifest a real bug. Warnings of
the kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is valid--considering the checks declared
in the API functions--but, still, it manifests discrepancy through
violation of an assertion declared in the test.\Mar{example!} In constrast, warnings
in the ``\lo{}'' group reflect the cases where the anomaly was
observed during the execution of functions not related to the test
itself. We found that different engines often check pre-conditions of
those functions differently. It can happen, for example, that one
engine enforces a weaker pre-condition on a function input compared to
another engine and that is acceptable.\Mar{example!} In those cases, our infrastructure would
observe a discrepancy that is more likely to be associated with an
invalid input produced by the fuzzer, \ie{}, it is likely to be a bug
in the test code not the engine (library or runtime) code. Although we
did find real bugs from ``\lo{}'' warnings, the proportion was much
lower compared to ``\hi{}'' warnings. Overall, only \Fix{12\%} of the
reals bugs we found originated from ``\lo{}'' warnings.

@@

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity, which is specially rich in this
domain. We report results in three parts. First, we report on the
stability of the engines we analyzed using the Test262 standard
conformance test suite for EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). The intuition is that the bugs we
discover throughout this study would have low relevance if the engines
are too fragile. Second, we report results obtained with test
transplantation (Section~\ref{sec:transplantation}). The rationale is
that the domain of possible inputs is too large; consequently, we
expect that test suites written for a given engine cover scenarios and
corner cases uncovered by another engine. To sum, we hope that that
test cases written for one engine could reveal bugs in different
engines as opposed to only manifesting false alarms such as those that
could emerge from implementation-dependent behavior. Third, we
analyzed the impact of using cross-engine differential testing to find
bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
rationale is that even black-box fuzzers that typicaly make valid
changes only in literals of the language could expose important
bugs. All in all, we want to assess the impact of simple approaches
that leverage on diversity to find bugs in \js\ engines with the goal
of assessing their reliability.

@@

We evaluated stability with Test262~\cite{ecma262-conformance-suite},
the official \js{} conformance test suite for the ECMA262
specification. We ran this suite once a day for seven consecutive
days. Table~\ref{tab:test262} shows the number of failures over this
period. It is important to note that failures are expected as it takes
time for engines to adjust to the spec. It is also important to
highlight that all engines we analyzed, but \chakra{}, use some
variant of the Test262 suite as part of their regression
process\Mar{with fewer tests?}. We used the official version
instead\Mar{, which updates tests regularly?}. To sum, we observed
that \Fix{...} \Mar{justify regressions using the kangax report}

@@

This section reports the results of test transplantion, \ie{}, we
analyzed the failures observed when running a test suite on an engine
other than the engine where the test suite
originated.

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 279 \\
    Duktape & 0 & 4 & 4 & 1   \\
    JerryScript & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
    Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

    %% \Igor{
    %%   For example, a testcase from \jsc{} suite explores the tail call
    %%   to optimize the recursion, the test uses a recursive function that
    %%   should be executed multiple times (ie. \mcodeid{1e6}). In this case, 
    %%   only the \jsc{} supports tail-call optimization and the testcase 
    %%   passes without failures. Another case can be found in JerryScript suite
    %%   that uses a repetition statement to concatenate long strings 
    %%   exponentially, causing an out of memory error. The engines used 
    %%   supports the flags to increase memory, however we prefer to use 
    %%   the default engine build.
    %% }

  \item \textbf{Not implemented.} False positives of this kind
    manifest when a test fails because it covers a function that is
    part of the official spec, but is not implemented in the target
    engine. For example, at the time of writing, Chakra does not
    implement by default various properties from the \mcodeid{Symbol}
    object. These properties are only available activating ES6
    experimental mode with the flag \CodeIn{-ES6Experimental}.

@@

An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
this is an intentional behavior of engine that crash the process if it runs out of memory.

>>>>

%% JavaScript (\js{}) is a popular programming language for the
%% web. Finding errors in JS runtime engines is an important problem.
\begin{abstract}
JavaScript is a very popular programming language today, permeating
different domains of application. Several JavaScript engines compete
for dominance and bugs on these engines are not rare. One important
reason for that is the language specification, which is incomplete and
evolves frequently.

This paper reports on a study to assess reliability
of JavaScript engines by leveraging the rich diversity of open-source
implementations. For that, we explored two methods---test
transplantation and cross-engine differential testing. Test
transplantation evaluates the effects of running test suites of a given
engine in another engine. Cross-engine differential testing evaluates
the effects of fuzzing existing inputs and then comparing the output
produced by different engines with a differential oracle.

Our results indicate that \Fix{...}
\end{abstract}

@@

JavaScript (\js{}) is today one of the most popular programming
languages around~\cite{business-insider,stackify}, with significant
penetration in various segments including, web development, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification
and implementations. It is natural to expect that such improvements
lead to sensible implementation changes. Even small changes can have
high practical impact. For example, in October 2014 a new attribute
added to Array objects resulted in the MS Outlook Calendar web app
stop working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
Intuitively, developing reliable engines is difficult because
specifications are incomplete and evolve frequently.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those
bugs. It\Comment{Finding bugs in \js\ engines} is also
challenging. For example, a test that passes in one engine could
legitimately fail in a different engine because of some undefined
behavior in the spec\footnote{These cases of undefined behavior can be
  localized by searching for the string ``implementation-dependent''
  in the ES6 spec document~\cite{ecmas262-spec}.}. As another example,
a test may fail because the engine does not fully implement some
feature. The publicly-available Kangax compatibility
table~\cite{kangax} relates features of \js\ with the engines that
support them. To sum, it is often non-trivial to assess if a test
fails because of a bug or because of some other reason making test
automation more challenging.

@@

%% WHAT WE DID
The goal of this paper is to assess reliability of popular
\js\ engines. The paper reports the results of a study that evaluates
the effectiveness of two complementary diversity-aware testing techniques. \emph{Test transplantation} leverages
diversity of test cases to find bugs. It evaluates the effects that
running \js{} test files from a given engine have in detecting bugs in
other engines. The intuition is that developers design test cases
differently; hence replaying the test in a different engine may reveal
unanticipated problems. \emph{Cross-engine differential testing}
evaluates the ability of leveraging diversity of engine
implementations to find bugs. More precisely, it fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. One of
various causes of output discrepancy is a bug. It is worth noting that
Differential Testing~\cite{Brumley-etal-ss07} (DT) has been applied in
a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files\footnote{These files are created with the grammar-based fuzzer
  jsfunfuzz~\cite{jsfunfuzz}. Look for option ``compare\_jit'' from funfuzz.} against different configurations of their
\smonkey{} engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across different configurations of the same build (\eg{}, enabling or
not eager JIT compilation). They use this technique since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
contrast, cross-engine differential testing--the technique used in
this work--checks functional correctness by comparing the output
produced by \emph{different engines} on a fuzzed
input~\cite{patra2016learning} as opposed to different builds of the
same engine. This approach has not been
popularized, certainly, because it is still not practical to fully automate--a
number of legitimate reasons exist, other than a bug, for a test
execution to manifest discrepancy (see
Table~\ref{tab:false-positives}). This study quantifies human effort
to find these bugs using this method.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed.}
  \begin{tabular}{cccr}
    \toprule
    Team & Name & URL & \# Stars \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{3300+} \\
    Google & \veight{} & \cite{v82018repo} & 9800+ \\
%    \jerry{} & \jerry{} & \cite{jerryscript2018repo} & 3100+ \\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ \\
%    Moddable & XS & \cite{xs2018repo} & 140+ \\
    %% \midrule
    %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{1100+} \\
   \bottomrule     
  \end{tabular}
\end{table}

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. Table~\ref{tab:test-suites} shows the breakdown of
tests we considered. Overall, we found a total of \totfiles{} JS
files. We did not consider tests from the \chakra{} repository because
they depend on non-portable objects. Notice that the number of tests
in \veight\ is low. That happens because many tests in \veight{} are
inherited from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. For all engines engines
we found test using non-portable functions that we detected by running
the test on a different engine. We needed to discard those.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites. The sections of the
    table show, respectively, the TC-39 conformance test suite, suites
    from engines we analyzed, and suites from other engines.}
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,021 \\
    \smonkey\ & \cite{mozilla} & 2,116 \\
    \veight{} & \cite{v8} & 57 \\
    \midrule    
    Duktape & \cite{duktape} & 921 \\ 
    \jerry{} & \cite{jerryscript} & 1,878 \\
    JSI & \cite{jsi} & 63 \\
    Tiny-js & \cite{tinyjs} & 37 \\    
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} \\
   \bottomrule     
  \end{tabular}
\end{table}

% For example to run the \jerry{} tests it was necessary 
% use the unit-test package to run it, but with our changes we added the assertion
% does not have an assertion in the test file
% \Fix{add code to explain}

@@

Generational fuzzers are typically grammar-based. These fuzzers
generate a new file using the grammar of the language whose inputs
should be fuzzed. Intuitively, those fuzzers implement a traversal of
the production rules of the input grammar to create syntax trees,
which are then pretty-printed. Consequently, this approach produces
inputs that are syntactically valid by construction. We analyzed four
grammar-based fuzzers--Grammarinator~\cite{grammarinator},
jsfunfuzz~\cite{jsfunfuzz},
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
were effective out of the box. For example, we produced 100K inputs
with Grammarinator and only \Fix{X} of those were valid. With
Megadeth, we were able to produce \Fix{Y, Y$>$Y?}  valid inputs as it
contains some heuristics to circumvent violations of certain type
rules such as \Fix{variable used must be defined?}. Nonetheless,
running those inputs in our infrastructure we were unable to find
discrepancies. Inspecting those inputs, we realized that they reflected
very simple scenarios. To sum, a high percentage of inputs that
Grammarinator and Megadeth generated were semantically-invalid that we
needed to discard whereas the valid inputs manifested no
discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
that, in addition to the issues mentioned above, it produces inputs
that use functions that are only available in the \smonkey{}
engine. We would need either to mock those functions in other engines
or to discard those tests. Considering
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
publicly available. One fundamental issue associated with generational
fuzzers in our context is that the tests they produce do not contain
assertions; to enable the integration of this kind of fuzzers in our
infrastructure, we would need to look for discrepancies across
compiler messages.  All in all, although grammar-based fuzzers have
been shown effective to find real
bugs~\cite{Holler:2012:FCF:2362793.2362831}, generating valid inputs,
albeit promising conceptually, still requires some engineering
effort. For this reason, we did not consider those fuzzers in this
study.

@@

Mutational fuzzers can be either white-box or black-box. White-box
mutational fuzzers are typically coverage-based. American Fuzz Loop
(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
kind of fuzzers. These fuzzers run tests inputs against instrumented
versions of the program under testing with the typical goal of finding
universal errors like crashes and buffer overflows. The instrumentation
adds code to collect branch coverage and to monitor specific
properties\footnote{There are options in the clang toolchain to build
  programs with fuzzing instrumentation~\cite{libfuzzer}. clang
  provides several sanitizers for property
  checking~\cite{clang-documentation}.}. AFL use coverage to determine
inputs that uncover a new branch and hence should be fuzzed more
whereas libFuzzer uses evolutionary generation--it tries to minimize
the distances to still-uncovered branches of the program. AFL takes
the instrumented program binary (say, a JS engine) and one seed input
to that program (say, a JS program) and produces on output
fault-revealing inputs, if found. Considering our context of
application, we needed to instrument one runtime engine for fuzzing;
we chose v8. Unfortunately, we found that most of the inputs produced
by AFL violate the JS grammar. Furthermore, the fuzzing task can take
days for a single seed input and there is no simple way to guide the
exploration\footnote{Exchanged emails with the tool author.}. That
happens because the fuzzer aims to explore the entire decision tree
induced from the engine's main function, including the branches
associated with the higher layers of the compiler (\eg{}, lexer and
parser). It is worth mentioning that Google mitigates that problem
with libFuzzer by asking developers to create fuzz targets for
specific program
functions\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
that approach has shown very effective, it requires domain knowledge
to create the calling context to invoke the fuzz target. For those
reasons, coverage-based fuzzers were not considered in this study.

We used two black-box mutational fuzzers in this
study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
\emph{existing} inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose \radamsa\ and
\quickfuzz\ \Fix{...elaborate...} \Mar{I mention below that these
  fuzzers ``only make valid changes in literals of the
  language''. Please confirm and explain that still this is
  interesting!}

\section{Differential Testing Infrastructure}
\label{sec:design}

@@

Recall that a warning can be manifested for reasons other than a bug
and there is no clear way to distinguish those cases automatically (see
Table~\ref{tab:false-positives}). A human needs to inspect the warning
to diagnose the discrepancy. To facilitate inspection, the
infrastructure prioritize these warnings and clusters them in
groups. Considering prioritization, we classified warnings in two
kinds, reflecting their likelihood to manifest a real bug. Warnings of
the kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is valid--considering the checks declared
in the API functions--but, still, it manifests discrepancy through
violation of an assertion declared in the test.\Mar{example!} In contrast, warnings
in the ``\lo{}'' group reflect the cases where the anomaly was
observed during the execution of functions not related to the test
itself. We found that different engines often check pre-conditions of
those functions differently. It can happen, for example, that one
engine enforces a weaker pre-condition on a function input compared to
another engine and that is acceptable.\Mar{example!} In those cases, our infrastructure would
observe a discrepancy that is more likely to be associated with an
invalid input produced by the fuzzer, \ie{}, it is likely to be a bug
in the test code not the engine (library or runtime) code. Although we
did find real bugs from ``\lo{}'' warnings, the proportion was much
lower compared to ``\hi{}'' warnings. Overall, only \Fix{12\%} of the
reals bugs we found originated from ``\lo{}'' warnings.

@@

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity, which is specially rich in this
domain. We report results in three parts. First, we report on the
stability of the engines we analyzed using the Test262 standard
conformance test suite for EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). The intuition is that the bugs we
discover throughout this study would have low relevance if the engines
are too fragile. Second, we report results obtained with test
transplantation (Section~\ref{sec:transplantation}). The rationale is
that the domain of possible inputs is too large; consequently, we
expect that test suites written for a given engine cover scenarios and
corner cases uncovered by another engine. To sum, we hope that that
test cases written for one engine could reveal bugs in different
engines as opposed to only manifesting false alarms such as those that
could emerge from implementation-dependent behavior. Third, we
analyzed the impact of using cross-engine differential testing to find
bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
rationale is that even black-box fuzzers that typically make valid
changes only in literals of the language could expose important
bugs. All in all, we want to assess the impact of simple approaches
that leverage on diversity to find bugs in \js\ engines with the goal
of assessing their reliability.

@@

We evaluated stability with Test262~\cite{ecma262-conformance-suite},
the official \js{} conformance test suite for the ECMA262
specification. We ran this suite once a day for seven consecutive
days. Table~\ref{tab:test262} shows the number of failures over this
period. It is important to note that failures are expected as it takes
time for engines to adjust to the spec. It is also important to
highlight that all engines we analyzed, but \chakra{}, use some
variant of the Test262 suite as part of their regression
process\Mar{with fewer tests?}. We used the official version
instead\Mar{, which updates tests regularly?}. To sum, we observed
that \Fix{...} \Mar{justify regressions using the Kangax report}

@@

This section reports the results of test transplantation, \ie{}, we
analyzed the failures observed when running a test suite on an engine
other than the engine where the test suite
originated.

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 279 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
    Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

    %% \Igor{
    %%   For example, a testcase from \jsc{} suite explores the tail call
    %%   to optimize the recursion, the test uses a recursive function that
    %%   should be executed multiple times (ie. \mcodeid{1e6}). In this case, 
    %%   only the \jsc{} supports tail-call optimization and the testcase 
    %%   passes without failures. Another case can be found in \jerry{} suite
    %%   that uses a repetition statement to concatenate long strings 
    %%   exponentially, causing an out of memory error. The engines used 
    %%   supports the flags to increase memory, however we prefer to use 
    %%   the default engine build.
    %% }

  \item \textbf{Not implemented.} False positives of this kind
    manifest when a test fails because it covers a function that is
    part of the official spec, but is not implemented in the target
    engine. For example, at the time of writing, \chakra{} does not
    implement by default various properties from the \mcodeid{Symbol}
    object. These properties are only available activating ES6
    experimental mode with the flag \CodeIn{-ES6Experimental}.

@@

An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
integer 3 to a big integer number. We reported this case in \chakra{} due a core dumps that occurs
during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
this is an intentional behavior of engine that crash the process if it runs out of memory.
